### 2020-06-14 report/sections/general/theory/lts.tex
Report: complete chapter 8.2

\item \rulename{Gr6}: 
\hl{TODO}
%The emission of a routed message $j$
%results in the message

\item \rulename{Gr7}:
\hl{TODO}

\item \rulename{Gr8}:
\hl{TODO}

\item \rulename{Gr9}:
\hl{TODO}

@@

@@

We explain rules \rulename{Lr4} and \rulename{Lr5}
from the perspective of role $\role{p}$.

@@

\item \rulename{Lr4}: 
\hl{TODO}

\item \rulename{Lr5}:
\hl{TODO}

@@

We explain rules \rulename{Lr6}, \rulename{Lr7},
\rulename{Lr10} and \rulename{Lr11}
from the perspective of role $\role{s}$.

@@

\item \rulename{Lr6}:
\hl{TODO}

\item \rulename{Lr7}:
\hl{TODO}

\item \rulename{Lr10}:
\hl{TODO}

\item \rulename{Lr11}:
\hl{TODO}

@@

We explain the remaining inductively defined rules.

\item \rulename{Lr8}:
\hl{TODO}

\item \rulename{Lr9}:
\hl{TODO}

>>>>

\item \rulename{Gr6} and \rulename{Gr7}
are analogue to \rulename{Gr1} and \rulename{Gr2}
for describing the emission and reception of
messages in routed communication, but uses
the ``routed in-transit'' construct instead.

\item \rulename{Gr8} and \rulename{Gr9}
are analogue to \rulename{Gr4} and \rulename{Gr5}
in the sense that we only enforce the
syntactic order of messages for the participants
involved in the action $l$.

@@

An important observation from
\rulename{Gr8} and \rulename{Gr9} is that,
for the router,
the syntactic order of routed communication
can be freely interleaved between
the syntactic order of direct communication.
This is a crucial result for proving
that the router does not over-serialise
communication -- 
we show this in \cref{subsection:encodepreservecomm}.

@@

We walk through rules \rulename{Lr4} and \rulename{Lr5}
from the perspective of role $\role{p}$.

@@

\item \rulename{Lr4} and \rulename{Lr5} are
analogue to \rulename{Lr1} and \rulename{Lr2}
for sending and receiving messages respectively.
The exception is that the new rules pattern-match
on the proxy role $\role{s}$ on the local type
and the routed label.

@@

We walk through rules \rulename{Lr6}, \rulename{Lr7},
\rulename{Lr10} and \rulename{Lr11}
from the perspective of role $\role{s}$.

@@

\item \rulename{Lr6} and \rulename{Lr7} are
analogue to \rulename{Gr1} and \rulename{Gr2}.
Intuitively, the router $\role{s}$ holds a
``global'' perspective on the interaction
between $\role{p}$ and $\role{q}$, which explains
the correspondence with the LTS semantics over global
types.

\item \rulename{Lr10} and \rulename{Lr11} allow
the router to perform routing actions before handling
their own direct communication. The syntax $l = \via{s}{\cdot}$
means that the label $l$ is ``of the form'' of a routing
action, i.e. there exists some $\role{p}, \role{q}, j$
such that $l = \via{s}{\aout{p}{q}{j}}$ or 
$l = \via{s}{\ain{p}{q}{j}}$.
The constraint of $\subj{l} \neq \mrole{q}$
prevents the violation of the syntactic order of messages
sent and received by $\mrole{q}$.

Curious readers can consider the examples 
$\proj{G_1}{s}$ and $\proj{G_2}{s}$
to see why this constraint is needed.

\begin{align*}
G_1 &= \gcommone{s}{r}{\tmsg{M1}} \grouteone{r}{q}{s}{\tmsg{M2}} \tend \\
\proj{G_1}{s} &= \tselone{r}{\tmsg{M1}}. ~ 
	\routerone{r}{q}{\tmsg{M2}}{\tend} \\~\\
G_2 &= \gcommone{s}{r}{\tmsg{M1}} \grouteone{p}{r}{s}{\tmsg{M2}} \tend \\
\proj{G_2}{s} &= \tselone{r}{\tmsg{M1}}. ~ 
	\routerone{p}{r}{\tmsg{M2}}{\tend} \\
\end{align*}

@@

As for the remaining rules,
\rulename{Lr8} and \rulename{Lr9} are analogue to
\rulename{Gr4} and \rulename{Gr5} because the router
holds a ``global'' perspective on the communication,
so transitions that do not violate the syntactic order
of messages between roles $\mrole{p}$ and $\mrole{q}$
are allowed.
